Multiresolution Neural Field Estimation

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
edits to discussion

The histogram in \figurename{\ref{fig:ParametersHistogram}} demonstrates the performance of the parameter estimation. \dean{The results are good because the RMSE between the true and estimated kernels is $1.83$ (units?)... There is a bias of 7.4 \% in $\theta_1$ because..., which is not big deal.}
\begin{figure}[!h]
 \centering
 \includegraphics[scale=1]{./Graph/ObservationFreqResponse.pdf}
 \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
functions (dashed lines), representing local excitation and lateral inhibition. (b) The average (over time) power in dB of the spatial frequency of the observations generated by the kernel in (a). The dashed line shows the cutoff frequency (-3 dB point).}
\label{fig:KernelAndFreqResponse} 
  \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Field.pdf}
 \caption{Spatial field at one time instant for different spatial resolutions, estimated and true fields are shown by dashed and solid lines respectively; (a) $j=0$, $n_x=17$. (b) $j=1$, $n_x=33$. (c) $j=2$, $n_x=65$. (d) $j=3$, $n_x=131$. (e) $j=4$, $n_x=263$.}
 \label{fig:FieldEstimates}
 \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Hist.pdf}
 \caption{(a) RMSE of the estimated field at different spatial scales. (b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively. The solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.}
 \label{fig:ParametersHistogram}
 \end{figure}

\section{Discussion}
Some discussion points
\begin{itemize}
	\item Brief summary of the novel aspects
	\item Discuss how we are improving the previous work
	\item Discuss heterogeneity and time delays (at larger spatial scales) and homogeneity (at smaller scales) 
	\item Discuss assumptions, limitations and future work
\end{itemize}

>>>>

The histogram in \figurename{\ref{fig:ParametersHistogram}} demonstrates the performance of the parameter estimation. \dean{The results are good because the RMSE between the true and estimated kernels is $1.83$ (units?)... There is a bias of 7.4 \% in $\theta_1$ because..., which is not big deal.}
\begin{figure}[!h]
 \centering
 \includegraphics[scale=1]{./Graph/ObservationFreqResponse.pdf}
 \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
functions (dashed lines), representing local excitation and lateral inhibition. (b) The average (over time) power in dB of the spatial frequency of the observations. The dashed line shows the cutoff frequency (-3 dB point).}
\label{fig:KernelAndFreqResponse} 
  \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Field.pdf}
 \caption{Actual (solid line) and estimated (dashed line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$. (b) $j=1$, $n_x=33$. (c) $j=2$, $n_x=65$. (d) $j=3$, $n_x=131$. (e) $j=4$, $n_x=263$.}
 \label{fig:FieldEstimates}
 \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Hist.pdf}
 \caption{(a) RMSE of the estimated field at different spatial scales. (b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively. The solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.}
 \label{fig:ParametersHistogram}
 \end{figure}

\section{Discussion}
In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...

This work extends previous work by... alternative ARMA model...

Other groups have previously highlighted the importance of a multiresolution approach in neural field modeling. For example, it is thought that the connectivity structure differs at different spatial scales, where at a fine scale a homogeneous connectivity exists and at a larger scale the connectivity become~\cite{Qubbaj2009}....

In order to apply the framework to real data several assumptions must be made, such as stationarity of the parameters over the estimation period. Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics. The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex. An obvious discrepancy is, for example, the linear activation function. Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation. Furthermore, the theory presented in this paper can be adapted to more sophisticated nonlinear forms of the field equations. The key development in this paper is the multiresolution decomposition forming the state-space model, which holds for a nonlinear activation function. If a nonlinear activation function was used, then unscented RTSS should be used in the E-step of the estimation algorithm.

Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions. Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model. Most importantly, future work should be directed towards applying and validating the framework on real data.
